Age-structured transmission dynamic models of RSV

### 2023-01-02 MSIS_model_explain/MSIS_model_explain.Rmd
add MLE section

>>>>

## Section 2: use maximum likelihood estimation (MLE) to estimate the unknown parameters

In this example, we will use maximum likelihood estimation (MLE) to estimate the (1) per capita transmission probability: baseline.txn.rate, (2) seasonal amplitude: Amp, (3) seasonal peak timing: phi, (4) duration of maternal immunity: DurationMatImmunityDays. 
\
\
We will treat the time-series and age distribution of RSV hospitalizations that we just simulated as observed status and calibrate our transmission dynamic models using MLE to estimate these "unknown" parameters.
